### 2017-01-18 Manuscripts/model-descriptions/jern-kemp-conjugate/jern-kemp-conjugate.tex
update

Working backwards, what is needed for simulation of exemplar generation is the probability of generating a stimulus $x$ given exposure to members of the target category $x_b$:
\
\begin{equation}
p(x | x_b) = ?
\end{equation}
\
where $x_b$ may be empty. Jern \& Kemp's model achieves this using a generative process. Category members ($x_a$ or $x_b$; more generally written as $x_y$) are assumed to have been generated using an underlying category distribution (specifically, multivariate normal):
\
\begin{equation}
  x_y \sim Normal(\mu_{y}, \Sigma_{y})
\end{equation}
\
$p(x | x_y)$ is proportional to the candidate's density under the target category's distribution. Thus, obtaining the category distribution parameters $(\mu_{y}, \Sigma_{y})$ is key for generation.

In Jern \& Kemp's original model, category distribution parameters are inferred exclusively from exposure to the category's members. To better simulate our paradigm, category distribution parameters (specifically, the $\Sigma_{y}$ parameter) in our implementation are also affected by a higher level domain distribution (specifically, Inverse-Wishart), from which $\Sigma_{y}$ are assumed to be generated:

\begin{equation}
  \Sigma_{y} \sim Wishart^{-1}(\Sigma_D, df_D)
\end{equation}
\
This document describes how we have obtained the relevant distributions.

\subsection*{Computing $\mu_y$}
Because Jern \& Kemp assume that the location of $x_y$ is independent of contrast categories, the category $\mu_{y}$ can be inferred exclusively based on exposure to the category's members. Assuming $(\mu_y, \Sigma_y)$ are Normal-Inverse-Wishart distributed (unknown mean, unknown variance):
\
\begin{equation}
  \mu_y = \dfrac
    {\kappa\mu_{0} + n_y \bar{x_y}}
    {\kappa + n_y}
    \label{eq:category_mus}
\end{equation}
\ 
where:
\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item $\mu_{0}$ is the prior mean along $p$ dimensions. Here we set it to the middle of the space.
    \item $\kappa$ is a scalar hyper-parameter, roughly weighting the importance of $\mu_{0}$. $\kappa$ must be greater than zero.
    \item $n_y$ is the number of observations in $x_y$
    \item $\bar{x_y}$ is the sample mean along $p$ dimensions
\end{itemize}

@@

\subsubsection*{Note}
In actuality, we ended up doing a bunch of matrix inverting that I do not understand:
\begin{verbatim}
Domain_Sigma = np.linalg.inv(Prior_Sigma)
for y in ncategories:
  Domain_Sigma += np.linalg.inv(Category_Sigmas[:,:,y])
Domain_Sigma = np.linalg.inv(Domain_Sigma)
\end{verbatim}
This is definitely not in the math, and I think it has something to do with Wishart vs. Inverse-Wishart. I think it also had something to do with the issue that its weird to just take the sum of the covariance matrices: the domain ends up assuming much larger covariances compared to any of the categories. We've never nailed it down. \textbf{Joe}, do you know what this is about?

@@

In previous versions, we sampled $\Sigma_y \sim Wishart^{-1}(\Sigma_D, df_D)$, with which we sampled $x \sim Normal(\mu_y, \Sigma_y)$. That was the approach taken by Jern \& Kemp. Sampling $x$, however, is not the primary goal of the model -- the main purpose of the model is to predict $p(x | x_b)$, and from those data we can sample $x$.

We could monte-carlo sample $x$ as described above to obtain $p(x | x_b)$. But this is computationally intensive, as each trial would need a separate sampler. Instead, it would be better to develop a method to infer $\Sigma_y$ without sampling.

>>>>

Working backwards, what is needed for simulation of exemplar generation is the probability of generating a stimulus $x$ given exposure to members of the target category $x_b$:
\
\begin{equation}
p(x | x_b) = ?
\end{equation}
\
where $x_b$ may be empty. Jern \& Kemp's model achieves this using a generative process. Category members ($x_a$ or $x_b$; more generally written as $x_y$) are assumed to have been generated using an underlying category distribution (specifically, multivariate normal):
\
\begin{equation}
  x_y \sim Normal(\mu_{y}, \Sigma_{y})
\end{equation}
\
$p(x | x_y)$ is proportional to the candidate's density under the target category's distribution. Thus, obtaining the category distribution parameters $(\mu_{y}, \Sigma_{y})$ is key for generation. This document describes how we compute these variables in a conjugate model.

\subsection*{Computing $\mu_y$}
Assuming $(\mu_y, \Sigma_y)$ are Normal-Inverse-Wishart distributed (unknown mean, unknown variance):
\
\begin{equation}
  \mu_y = \dfrac
    {\kappa\mu_{0} + n_y \bar{x_y}}
    {\kappa + n_y}
    \label{eq:category_mus}
\end{equation}
\ 
where:
\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item $\mu_{0}$ is the prior mean along $p$ dimensions. Here we set it to the middle of the space.
    \item $\kappa$ is a scalar hyper-parameter, roughly weighting the importance of $\mu_{0}$. $\kappa$ must be greater than zero.
    \item $n_y$ is the number of observations in $x_y$
    \item $\bar{x_y}$ is the sample mean along $p$ dimensions
\end{itemize}

@@

Thus, categories are assumed to have some degree of variance along each feature (specified by $\gamma$), but not are assumed to possess feature-feature correlations.

@@
